Molecular dynamics simulation of synchronization in driven particles

### 2021-03-26 manuscript/manuscript_ajp_version2.tex
updated page numbers

\section{Introduction} 
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli.\cite{Pikovsky2003}
The
flickering patterns of
candle flames ]xx is a flame an oscillator? xx] mediated by temperature fluctuations,\cite{Okamoto2016}
the vibrations of singing wine glasses interacting 
through sound waves,\cite{Arane2009}
and metronomes vibrating through a supporting platform\cite{Jia2015}
are examples of in-phase coupled oscillations. 
Biological systems benefit from cooperative
synchronization --
birds coordinate wing flaps
to optimize energy use during flight,\cite{Portugal2014}
frogs alternate croaking patterns,\cite{Aihara2014}
humans clap in time with music,\cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle\cite{MartinHall1999}
and brain tissue.\cite{Singer1999}
External forcing can cause or regulate 
synchronization. For example, 
an electrical pacemaker 
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies.

@@

The confining force on the particle %[DM removed subscripts] $i$
 is given by
 \begin{equation}
 \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U^{\ell}(\vec{r}).
 \label{eq:dudr}
 \end{equation}
 %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
 In Fig.~\ref{fig:1_landscape}(b) we plot  
 $U(y)$ to illustrate how the magnitude
 $|\vec{F}^{\ell}|$ is calculated from the particle position $y$.
 %[My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.  This is consistent with the textbook I teach from.  xx suggest that you use subscripts instead of superscripts. We can easily make that change in the next iteration of your manuscript. However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$. One of us didn't like superscripts where he was an undergraduate!  xx]

@@

The equation of motion provides a direct calculation of the velocity
of an individual particle at position $\vec{r}$ 
and simulation time $t$.
The   simulation is controlled by a  loop
which runs to a maximum integer time step.
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}(t)$
and then integrate
the equation of motion to move particles
to an updated position.
Because the acceleration is zero,
the integration of the equation of motion
is performed via 
the simple first-order Euler method 
\begin{equation}
  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
    \label{eq:euler}
\end{equation}
for a time step $\Delta t = 0.1\,\tau$.
In 
Problem~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%------------------------------------------------------------------
\begin{figure} % [h!]
\centering
\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
\caption{
Schematic of the simulation of a single particle
  driven across a washboard potential energy landscape.
  (a) View of the $x$-$y$ plane. 
  The time-dependent applied driving force $\vec{F}^{\rm d}$
  is parallel to the $y$-axis.
  The landscape is shown with 
  maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is 
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the $y$-axis $U^{\ell}(y)$.  
  The particle in (a) is shown at the same $y$-position.
  The slope of $U^{\ell}(y)$ %[DM use the subscripts with the potential, but will move to superscript xx used subscript here xx]
  is the 
  magnitude of force $\vec{F}^{\ell}$. 
  }
\label{fig:1_landscape}
\end{figure}
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:results}
Here we drive 
a single particle 
across the landscape. 
The numerical implementation of the landscape 
is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  %[DM - right, two negative signs, one from the derivative, the other from the definition of force.  I found the ``mistaken'' dropped minus sign in the depths of january and added it.  xx but you should get a + sign not a minus sign xx] 
\begin{equation}
  \label{eq:force}
  F^\ell_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
\end{equation}
where the force is scaled by the parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1\,F_0$ 
with $N_p=20$ minima, 
corresponding to a spatial period $\lambda = 2.3\,a_0$.
The competition between the driving force and the landscape potential
can produce a variety of hopping patterns in the particle motion. 
The relative values of $F^{\rm ac}$, $F^{\rm dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
If $F^{\rm d}(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
If the driving frequency is low,
as in Fig.~\ref{fig:2_Fd_vy_time},  
the driven particle 
moves 
in a pattern 
with the same frequency 
as the time-dependent force $F^{\rm d}(t)$,
but is modulated by the landscape period.
We explore changes in the frequency and different values of $F^{\rm ac}$ 
in Problem~\ref{ex:parameters}.
Here we vary $F^{\rm dc}$ 
while holding the remaining parameters fixed.

@@

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities 
  in a two-dimensional phase plot. 
  For a driven pendulum confined to a single potential well,
  an appropriate
  phase space is the particle velocity $v_y$ versus the position $y$.  
  For a particle driven 
  through multiple identical wells 
  we define phase variables 
  to account for the net increase in the position.
  The phase position is
  \begin{equation}
    \phi(t) = 2\pi [y(t)-\langle v_y \rangle t]/\lambda,
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$.\cite{Juniper2015}
  The phase velocity is
  \begin{equation}
    \dot{\phi}(t) =2\pi [v_y(t)-\langle v_y \rangle] /\lambda.  
  \end{equation}
  For zero landscape force, 
  the phase velocity  is zero when $F^{\rm d}(t) = F^{\rm dc}$.
  If the velocity
  is mode-locked to 
  a spatial location, [xx don't understand meaning of the velocity
  is mode-locked to 
  a spatial location xx]
  a closed loop appears in  
  phase space. 
  A 1:1 mode appears as a circle or oval. 
  Nodes appear 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an almost closed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relation
  shifts in time as in Fig.~\ref{fig:4_phase}.

  In Fig.~\ref{fig:4_phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing 
  $F^{\rm dc}$, 
  with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
 [xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
For
  $F^{\rm dc} = 0.04$
  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is a small [xx not clear what small means? can we eliminate this word? xx] asymmetric curve.
  A tail appears
  due to the initial transient
  motion of the particle.
  The particle is confined to a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{\rm dc}$.
  In Fig.~\ref{fig:4_phase}(b)
  with $F^{\rm dc} = 0.07$
  the phase loop is a symmetric triangular shape,
  indicating a 1:1 match between the
  particle motion and velocity consistent with 
  Fig.~\ref{fig:2_Fd_vy_time}(a).
  As $F^{\rm dc}$ is
  increased,
  nodes form in the phase diagram, which
   occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  In Fig.~\ref{fig:4_phase}(c)
  with $F^{\rm dc} = 0.1$
  two nodes form.
  The particle moves a distance $2\lambda$
  during one time period.
For $F^{\rm dc} = 0.125$ as in Fig.~\ref{fig:4_phase}(d),
  three nodes form as the particle moves across $3\lambda$.

@@

In Ref.~\onlinecite{Juniper2015}
  experiments with single colloids 
  produce 
  the following
  combinations of forward and backward steps
  by sweeping through
  a variety of applied forces parameters $F^{\rm dc}$ and $F^{\rm ac}$:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}
  we fix $f=0.01$, $F^{\rm dc}=0.07$, and $A_p = 0.1$,
  and increase
  the amplitude of $F^{\rm ac}$.
  This increase causes the number of backward steps to increase.
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^{\rm d}(t)$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
  $F^{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
  the number of backward steps
  $n_b = 0$ with $n_f = 4$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F^{\rm ac} = 0.4$
  $n_b = 2$ and $n_f = 6$.
  In each case the average velocity 
  is $\langle v_y \rangle = 4\lambda f$,
  which can be reproduced over a variety of $F^{\rm ac}$ values. [xx what is the question? leave something to the reader! xx]

@@

  In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
  with a period of $45\,\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\,\tau$).
  At an intermediate frequency 
  such as $f=0.01$,
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  In Fig.~\ref{fig:6_freq}(c) $f=0.005$
  the particle hops forward two minima for every period of $200\,\tau$.
  Low frequencies
  result in a sustained positive motion of a particle.
  In Fig.~\ref{fig:6_freq}(e) $f=0.001$
  the hopping is continuous
  over the time $100\,\tau < t < 400\,\tau$,
  with the cycle repeating 
  over the period length $1000\,\tau$. [xx same comment. too much information xx]

@@

\noindent Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of the forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i,
  \label{eq:n2l}
  \end{equation}
  where $m_i$ is the
  inertial mass.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  by a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{\rm drag} = - \gamma \vec{v}_i$,
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Problem~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is 
  known as the momentum relaxation time,
  and is small for
  particles with low Reynolds numbers.
  The mass of a
  typical colloid particle is $15$\,picograms,
  leading to a momentum relaxation time
  on the order of microseconds.

@@

\item [(b)] If $m/\gamma$ is small, the
  particle's acceleration can be ignored
  entirely.
Using Newton's second law for
  a small momentum relaxation time, 
  show that a particle confined to a landscape exerting force
  $F^\ell(\vec{r}_i)$ subject to a time dependent drive $F^{\rm d}(t)$
  can be modeled by the equation of motion described in 
  Eq.~\eqref{eq:motion}.
  \end{enumerate}
\end{problem}

\begin{problem}{Integration methods}
  \label{ex:euler}
[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK. Instead you might want to make this problem 1 and guide  readers to write their own program. Then mention that a program is available, which you only mention in the abstract xx]

To calculate the position of the particle we
  numerically integrate the equation of motion using
  the standard definition of velocity
  $\vec{v}_i = d\vec{r}_i/dt$ 
  using the 
  Euler method. 
  The equation of motion provides
  a direct calculation for the particle velocity,
  as demonstrated in Problem~\ref{ex:n2l}.  
The Euler method is effective for solving linear ordinary differential  equations
  of the form
  $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a  solution of a map using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
 Apply the Euler method to our equation
  of motion [xx refer to specific equation by label xx] to determine  the analytic expression
for the position of a particle
  $y_n$ at the $nth$ time step.

@@

[xx AJP requires last page numbers for papers xx] 
\begin{thebibliography}{99}

@@

\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima, ``Synchronization in flickering of three-coupled candle flames," Sci. Rep. {\bf 6}, 36145--xx (2016).

\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--xx (2009). %; https://doi.org/10.1119/1.3119175

\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and J. Xiao, ``Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes," Sci. Rep. {\bf 5}, 17008--xx (2015).

%Synchronization of a thermoacoustic oscillator by an external sound source
%G. Penelet and T. Biwa
%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189

  %biological examples

@@

  \bibitem{Aihara2014} I. Aihara, T. Mizumoto, T. Otsuka, H. Awano, K. Nagira, H. G. Okuno and K. Aihara, ``Spatio-temporal dynamics in collective frog choruses examined by mathematical modeling and field observations," Sci. Rep. {\bf 4}, 3891--xx (2014).

@@

  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563--xx (2002).

  %colloids
  \bibitem{Pertsinidis2001} A. Pertsinidis and X. Ling,  ``Equilibrium configurations and energetics of point defects in two-dimensional colloidal crystals," Phys Rev. Lett.  {\bf 87}, 098303-1--xx (2001). %https://doi.org/10.1103/PhysRevLett.87.098303

  \bibitem{Juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, ``Microscopic dynamics of synchronization in driven colloids," Nat. Commun. 6, 7187--xx (2015); 
      %\bibitem{Juniper2018}

@@

  \bibitem{Reichhardt2015} C. Reichhardt, and C. J. O. Reichhardt,  ``Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives," Phys. Rev. B {\bf 92} (22), 224432-1--xx (2015).

@@

  %chaos!
  \bibitem{Bak1986} P. Bak. ``The Devil's staircase," Physics Today {\bf 39}(12), 38--xx (1986).

@@

    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--xx (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).

   %Josephson Junctions and other condensed matter applications
    \bibitem{Shapiro1963} S. Shapiro, ``Josephson currents in superconducting tunneling: The effect of microwaves and other observations," Phys. Rev. Lett. {\bf 11}, 80--xx (1963).

    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev, ``The current-phase relation in Josephson junctions," Rev. Mod. Phys. {\bf 76}, 411--xx (2004).

    \bibitem{Benz1990}  S. P. Benz, M. S. Rzchowski, M. Tinkham, and C. J. Lobb, ``Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays," Phys. Rev. Lett. {\bf 64}, 693--xx (1990); D. Dom{\'i}nguez and J. V. Jos{\'e}, ``Giant Shapiro steps with screening currents," Phys. Rev. Lett. {\bf 69}, 514--xx (1992).

>>>>

\section{Introduction} 
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli.\cite{Pikovsky2003}
The
flickering patterns of
candle flames %[DM - the air molecules are oscillating I think xx is a flame an oscillator? xx]
mediated by temperature fluctuations,\cite{Okamoto2016}
the vibrations of singing wine glasses interacting 
through sound waves,\cite{Arane2009}
and metronomes vibrating through a supporting platform\cite{Jia2015}
are examples of in-phase coupled oscillations. 
Biological systems benefit from cooperative
synchronization --
birds coordinate wing flaps
to optimize energy use during flight,\cite{Portugal2014}
frogs alternate croaking patterns,\cite{Aihara2014}
humans clap in time with music,\cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle\cite{MartinHall1999}
and brain tissue.\cite{Singer1999}
External forcing can cause or regulate 
synchronization. For example, 
an electrical pacemaker 
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies.

@@

The confining force on the particle %[DM removed subscripts] $i$
 is given by
 \begin{equation}
 \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
 \label{eq:dudr}
 \end{equation}
 %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
 In Fig.~\ref{fig:1_landscape}(b) we plot  
 $U(y)$ to illustrate how the magnitude
 $|\vec{F}^{\ell}|$ is calculated from the particle position $y$.
 %[My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.  This is consistent with the textbook I teach from.  xx suggest that you use subscripts instead of superscripts. We can easily make that change in the next iteration of your manuscript. However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$. One of us didn't like superscripts where he was an undergraduate!  xx]

@@

The equation of motion provides a direct calculation of the velocity
of an individual particle at position $\vec{r}$ 
and simulation time $t$.
The   simulation is controlled by a  loop
which runs to a maximum integer time step.
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}(t)$
and then integrate
the equation of motion to move particles
to an updated position.
Because the acceleration is zero,
the integration of the equation of motion
is performed via 
the simple first-order Euler method 
\begin{equation}
  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
    \label{eq:euler}
\end{equation}
for a time step $\Delta t = 0.1\,\tau$.
In 
Problem~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%------------------------------------------------------------------
\begin{figure} % [h!]
\centering
\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
\caption{
Schematic of the simulation of a single particle
  driven across a washboard potential energy landscape.
  (a) View of the $x$-$y$ plane. 
  The time-dependent applied driving force $\vec{F}^{\rm d}$
  is parallel to the $y$-axis.
  The landscape is shown with 
  maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is 
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the $y$-axis $U(y)$.  %DM removed ^{\ell}
  The particle in (a) is shown at the same $y$-position.
  The slope of $U(y)$ %[DM removed ^{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
  is the 
  magnitude of force $\vec{F}^{\ell}$. 
  }
\label{fig:1_landscape}
\end{figure}
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:results}
Here we drive 
a single particle 
across the landscape. 
The numerical implementation of the landscape 
is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  %[DM - right, two negative signs, one from the derivative, the other from the definition of force.  I found the ``mistaken'' dropped minus sign in the depths of january and added it.  xx but you should get a + sign not a minus sign xx] 
\begin{equation}
  \label{eq:force}
  F^\ell_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
\end{equation}
where the force is scaled by the parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1\,F_0$ 
with $N_p=20$ minima, 
corresponding to a spatial period $\lambda = 2.3\,a_0$.
The competition between the driving force and the landscape potential
can produce a variety of hopping patterns in the particle motion. 
The relative values of $F^{\rm ac}$, $F^{\rm dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
If $F^{\rm d}(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
If the driving frequency is low,
as in Fig.~\ref{fig:2_Fd_vy_time},  
the driven particle 
moves 
in a pattern 
with the same frequency 
as the time-dependent force $F^{\rm d}(t)$,
but is modulated by the landscape period.
We explore changes in the frequency and different values of $F^{\rm ac}$ 
in Problem~\ref{ex:parameters}.
Here we vary $F^{\rm dc}$ 
while holding the remaining parameters fixed.

@@

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities 
  in a two-dimensional phase plot. 
  For a driven pendulum confined to a single potential well,
  an appropriate
  phase space is the particle velocity $v_y$ versus the position $y$.  
  For a particle driven 
  through multiple identical wells 
  we define phase variables 
  to account for the net increase in the position.
  The phase position is
  \begin{equation}
    \phi(t) = 2\pi [y(t)-\langle v_y \rangle t]/\lambda,
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$.\cite{Juniper2015}
  The phase velocity is
  \begin{equation}
    \dot{\phi}(t) =2\pi [v_y(t)-\langle v_y \rangle] /\lambda.  
  \end{equation}
  For zero landscape force, 
  the phase velocity  is zero when $F^{\rm d}(t) = F^{\rm dc}$.
  %[DM rewrite]
  If the system
  is strictly mode-locked,
  the particle velocity
  recurs at a particular spatial location, and 
  %If the velocity
  %is mode-locked to 
  %a spatial location,
  %[xx don't understand meaning of the velocity
  %is mode-locked to 
  %a spatial location xx]
  a closed loop appears in  
  phase space. 
  A 1:1 mode appears as a circle or oval. 
  Nodes appear 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an almost closed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relation
  shifts in time as in Fig.~\ref{fig:4_phase}.

  In Fig.~\ref{fig:4_phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing 
  $F^{\rm dc}$, 
  with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
 %[xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
  For
  $F^{\rm dc} = 0.04$
  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is an
  % small [xx not clear what small means? can we eliminate this word? xx]
  asymmetric curve.
  A tail appears
  due to the initial transient
  motion of the particle.
  The particle is confined to a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{\rm dc}$.
  In Fig.~\ref{fig:4_phase}(b)
  with $F^{\rm dc} = 0.07$
  the phase loop is a symmetric triangular shape,
  indicating a 1:1 match between the
  particle motion and velocity consistent with 
  Fig.~\ref{fig:2_Fd_vy_time}(a).
  As $F^{\rm dc}$ is
  increased,
  nodes form in the phase diagram, which
   occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  In Fig.~\ref{fig:4_phase}(c)
  with $F^{\rm dc} = 0.1$
  two nodes form.
  The particle moves a distance $2\lambda$
  during one time period.
For $F^{\rm dc} = 0.125$ as in Fig.~\ref{fig:4_phase}(d),
  three nodes form as the particle moves across $3\lambda$.

@@

In Ref.~\onlinecite{Juniper2015}
  experiments with single colloids 
  produce 
  the following
  combinations of forward and backward steps
  by sweeping through
  a variety of applied forces parameters $F^{\rm dc}$ and $F^{\rm ac}$:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}
  we fix $f=0.01$, $F^{\rm dc}=0.07$, and $A_p = 0.1$,
  and increase
  the amplitude of $F^{\rm ac}$.
  This increase causes the number of backward steps to increase.
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^{\rm d}(t)$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
  $F^{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
  the number of backward steps
  $n_b = 0$ with $n_f = 4$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F^{\rm ac} = 0.4$
  $n_b = 2$ and $n_f = 6$.
  In each case the average velocity 
  is $\langle v_y \rangle = 4\lambda f$,
  which can be reproduced over a variety of $F^{\rm ac}$ values.
  %[xx what is the question? leave something to the reader! xx]

@@

  In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
  with a period of $45\,\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\,\tau$).
  At an intermediate frequency 
  such as $f=0.01$,
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  In Fig.~\ref{fig:6_freq}(c) $f=0.005$
  the particle hops forward two minima for every period of $200\,\tau$.
  Low frequencies
  result in a sustained positive motion of a particle.
  In Fig.~\ref{fig:6_freq}(e) $f=0.001$
  the hopping is continuous
  over the time $100\,\tau < t < 400\,\tau$,
  with the cycle repeating 
  over the period length $1000\,\tau$.
  %[xx same comment. too much information xx]

@@

\noindent Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of the forces on the particle 
  \begin{equation}
  m \vec{a} = \sum \vec{F},
  \label{eq:n2l}
  \end{equation}
  where $m$ is the
  inertial mass.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  by a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{\rm drag} = - \gamma \vec{v}$,
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Problem~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is 
  known as the momentum relaxation time,
  and is small for
  particles with low Reynolds numbers.
  The mass of a
  typical colloid particle is $15$\,picograms,
  leading to a momentum relaxation time
  on the order of microseconds.

@@

\item [(b)] If $m/\gamma$ is small, the
  particle's acceleration can be ignored
  entirely.
Using Newton's second law for
  a small momentum relaxation time, 
  show that a particle confined to a landscape exerting force
  $F^\ell(\vec{r})$ subject to a time dependent drive $F^{\rm d}(t)$
  can be modeled by the equation of motion described in 
  Eq.~\eqref{eq:motion}.
  \end{enumerate}
\end{problem}

\begin{problem}{Integration methods}
  \label{ex:euler}
%[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK. Instead you might want to make this problem 1 and guide  readers to write their own program. Then mention that a program is available, which you only mention in the abstract xx]

To calculate the position of the particle we
  numerically integrate the equation of motion using
  the standard definition of velocity
  $\vec{v} = d\vec{r}/dt$ 
  using the 
  Euler method. 
  The equation of motion provides
  a direct calculation for the particle velocity,
  as demonstrated in Problem~\ref{ex:n2l}.  
The Euler method is effective for solving linear ordinary differential  equations
  of the form
  $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a  solution of a map using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  Apply the Euler method to %our equation of motion
  Eq.~\ref{eq:motion}
  %[xx refer to specific equation by label xx]
  to determine  the analytic expression
  for the position of a particle
  $y_n$ at the $nth$ time step.

@@

%%[xx AJP requires last page numbers for papers xx] 
\begin{thebibliography}{99}

@@

\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima, ``Synchronization in flickering of three-coupled candle flames," Sci. Rep. {\bf 6}, 36145--36155 (2016).

\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--1067 (2009). %; https://doi.org/10.1119/1.3119175

\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and J. Xiao, ``Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes," Sci. Rep. {\bf 5}, 17008--17020 (2015).

%Synchronization of a thermoacoustic oscillator by an external sound source
%G. Penelet and T. Biwa
%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189
  %biological examples

@@

  \bibitem{Aihara2014} I. Aihara, T. Mizumoto, T. Otsuka, H. Awano, K. Nagira, H. G. Okuno and K. Aihara, ``Spatio-temporal dynamics in collective frog choruses examined by mathematical modeling and field observations," Sci. Rep. {\bf 4}, 3891--3899 (2014).

@@

  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563–579 (2002).

  %colloids
  \bibitem{Pertsinidis2001} A. Pertsinidis and X. Ling,  ``Equilibrium configurations and energetics of point defects in two-dimensional colloidal crystals," Phys Rev. Lett.  {\bf 87}, 098303-1--4 (2001). %https://doi.org/10.1103/PhysRevLett.87.098303

  \bibitem{Juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, ``Microscopic dynamics of synchronization in driven colloids," Nat. Commun. 6, 7187--7194 (2015); 
      %\bibitem{Juniper2018}

@@

  \bibitem{Reichhardt2015} C. Reichhardt, and C. J. O. Reichhardt,  ``Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives," Phys. Rev. B {\bf 92} (22), 224432-1--12 (2015).

@@

  %chaos!
  \bibitem{Bak1986} P. Bak. ``The Devil's staircase," Physics Today {\bf 39}(12), 38--45 (1986).

@@

    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--362 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).

   %Josephson Junctions and other condensed matter applications
    \bibitem{Shapiro1963} S. Shapiro, ``Josephson currents in superconducting tunneling: The effect of microwaves and other observations," Phys. Rev. Lett. {\bf 11}, 80--82 (1963).

    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev, ``The current-phase relation in Josephson junctions," Rev. Mod. Phys. {\bf 76}, 411--469 (2004).

    \bibitem{Benz1990}  S. P. Benz, M. S. Rzchowski, M. Tinkham, and C. J. Lobb, ``Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays," Phys. Rev. Lett. {\bf 64}, 693--696 (1990); D. Dom{\'i}nguez and J. V. Jos{\'e}, ``Giant Shapiro steps with screening currents," Phys. Rev. Lett. {\bf 69}, 514--517 (1992).
